Analysis paper

### 2021-06-17 analysis/analysis.Rmd
update plots

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model", fill = "model")) + 
    # geom_density_ridges(aes(fill = model, color = NA),
    #                     rel_min_height = 0.005,
    #                     scale = 0.9,
    #                     # jittered_points = TRUE,
    #                     # position = position_points_jitter(width = 0.05, height = 0),
    #                     point_size = 1.5,
    #                     point_shape = 21,
    #                     #point_shape = '|',
    #                     point_alpha = 1,
    #                     alpha = 0.3) +
    ggdist::stat_dots(aes(color = model)) + 
    ggdist::stat_pointinterval(point_interval = mean_qi, size = 3, shape = 16, fill = "black", .width = NA) + 
    ggdist::stat_pointinterval(point_interval = median_qi, size = 3, shape = 15, fill = "black", .width = NA) + 
        facet_wrap(~ target_type, ncol = 1, scales = "free") + 
    theme(plot.margin=unit(c(0,0.4,0,0),"cm")) +
    # geom_density_ridges(quantile_lines=TRUE,
    #                     quantile_fun=function(x,...) mean(x), 
    #                     linetype = "dotted", 
    #                     alpha = 0, 
    #                     scale = 0.9, 
    #                     rel_min_height = 0.01) +
    scale_fill_manual(values = coldeaths) + 
    scale_color_manual(values = coldeaths) + 
    # scale_color_manual(aesthetics = "point_color", 
    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Model", x = "Weighted interval score") + 
  scale_x_continuous(labels = scales::label_number(suffix = "k", 
                                                   scale = 1e-3, 
                                                   accuracy = NULL)) + 
    theme_light()
}

>>>>

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model", fill = "model")) + 
    # geom_density_ridges(aes(fill = model, color = NA),
    #                     rel_min_height = 0.005,
    #                     scale = 0.9,
    #                     # jittered_points = TRUE,
    #                     # position = position_points_jitter(width = 0.05, height = 0),
    #                     point_size = 1.5,
    #                     point_shape = 21,
    #                     #point_shape = '|',
    #                     point_alpha = 1,
    #                     alpha = 0.3) +
    ggdist::stat_slab(alpha = 0.3, scale = 0.8, normalize = "panels") +
  # ggridges::geom_density_ridges(aes(color = NA), scale = 1.3) + 
    ggdist::stat_dots(aes(color = model)) + 
    ggdist::stat_pointinterval(point_interval = mean_qi, size = 3, shape = 16, fill = "black", .width = NA) + 
    ggdist::stat_pointinterval(point_interval = median_qi, size = 3, shape = 15, fill = "black", .width = NA) + 
        facet_wrap(~ target_type, ncol = 1, scales = "free") + 
    theme(plot.margin=unit(c(0,0.4,0,0),"cm")) +
    # geom_density_ridges(quantile_lines=TRUE,
    #                     quantile_fun=function(x,...) mean(x), 
    #                     linetype = "dotted", 
    #                     alpha = 0, 
    #                     scale = 0.9, 
    #                     rel_min_height = 0.01) +
    scale_fill_manual(values = coldeaths) + 
    scale_color_manual(values = coldeaths) + 
    # scale_color_manual(aesthetics = "point_color", 
    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Model", x = "Weighted interval score") + 
  scale_x_continuous(labels = scales::label_number(suffix = "k", 
                                                   scale = 1e-3, 
                                                   accuracy = NULL)) + 
    theme_light()
}
